COMPJ-2022-05-0325: Response to referees

### 2023-05-12 paper-seb-main.tex
Made final reference column balance

\indented 3
``Software Engineering Boards,'' analogous to Ethics or Institutional Review Boards, should be instigated and used.

\indented 4
The Reproducible Analytic Pipeline (RAP) methodology can be generalized to cover code and Software Engineering methodologies, in a generalization this paper introduces called \RAPstarp. \RAPstar\ (or comparable interventions) could be supported and or even required in journal, conference, and funding body policies.

@@

\bibnewcolumn = 112 % bibentry number of last entry on (final) left hand column
% Hint: set it to a very large number, so the final column is as unbalanced as it gets
% then, if it's worth fixing the final page, lower the number to some citation on the 
% lower part of the left hand column; this citation will then become the last in that
% column. Hopefully the righthand column will be of equal length!
% PS Don't forget to check there is nothing on the following page!

@@

% I haven't figured out how to make the \labelwidth etc variable - it'd be nice
% to have it suitable for numbers up to 9, then for numbers up to 99, then up to 999
% depending on the largest bibitem number width in the column. As it is, it's set
% to the width of 999 for all bibitems even though it takes a while for bibitems to get 
% up to 3 figures. Sigh

>>>>

\indented 2
``Software Engineering Boards,'' analogous to Ethics or Institutional Review Boards, should be instigated and used.

\indented 3
The Reproducible Analytic Pipeline (RAP) methodology can be generalized to cover code and Software Engineering methodologies, in a generalization this paper introduces called \RAPstarp. \RAPstar\ (or comparable interventions) could be supported and or even required in journal, conference, and funding body policies.

@@

\bibnewcolumn = 122 % bibentry number of last entry on (final) left hand column
% Hint: set it to a very large number, so the final column is as unbalanced as it gets
% then, if it's worth fixing the final page, lower the number to some citation on the 
% lower part of the left hand column; this citation will then become the last in that
% column. Hopefully the righthand column will be of equal length!
% PS Don't forget to check there is nothing on the following page!

@@

% I haven't figured out how to make the \labelwidth etc variable - it'd be nice
% to have it suitable for numbers up to 9, then for numbers up to 99, then up to 999
% depending on the largest bibitem number width in the column. As it is, it's set
% to the width of 999 for all bibitems even though it takes a few pages for bibitems to get 
% up to 3 figures. Sigh

### 2023-05-12 response-to-referees/response 12 May 2023.tex
Made final reference column balance

\newnote{There are a few remaining typos}{Thanks. I've reviewed the entire paper very carefully, and of course benefitted from all the referees' careful reading and pointing out of typos, all of which I have fixed.}

\nonote{\ldots\ including one sentence where you may have omitted a ``not'', thereby reversing what you intended to say. (I regret that I have been unable to find this again --- please check. I think it was toward the bottom of a paragraph in the left-hand column.)}{}

>>>>

\newnote{There are a few remaining typos}{Thanks. I've reviewed the entire paper very carefully, and of course benefitted from all the referees' careful reading and pointing out of typos, all of which I have fixed --- I trust this covers all the typos you were concerned about.}

\newnote{\ldots\ including one sentence where you may have omitted a ``not'', thereby reversing what you intended to say. (I regret that I have been unable to find this again --- please check. I think it was toward the bottom of a paragraph in the left-hand column.)}{In addition to implementing all the corrections the referees suggested, I have re-read my paper carefully several times, but I have not found this problem.}
